---
title: "Final Project"
author: "Andrew Edelblum, Kivalina Grove, and Ouafaa Hmaddi"
date: "5/20/2019"
output: html_document
---

```{r cleanup, include = FALSE}
library(rio)
library(tidyverse)
library(janitor)
library(colorblindr)
library(stringr)

d <- import("./MasterKickstarter.csv", setclass = "tbl_df") %>% 
     clean_names()

lower48 <- d %>% 
           select(-1:-3) %>% 
           filter(launched_at_y == 13 & 
                  country == "USA" & 
                  county != "Non-USA" & 
                  state != "Non-USA" &
                  status != "canceled") %>% 
           mutate(categories = as.factor(categories))

levels(lower48$categories) <- sub("film%20&%20video", "film", levels(lower48$categories))

lower48 <- data.frame(lapply(lower48, function(lower48) { #Simple, but effective use of if/else logic!
           if (is.character(lower48)) return(tolower(lower48))
           else return(lower48)
}))

# We looked at inverse of filter to see which cases were in USA == country but were also labeled as county != Non-USA. Those cases were those that were not part of the continental US. We are only looking at Kickstarter campaigns on 2013.
```

```{r split}
lower48_split <- lower48 %>% 
                 split(paste(lower48$state))

lower48_nest <- lower48 %>%
                group_by(state) %>%
                nest() %>%
                mutate(plot = map2(data, state, ~ggplot(.x, aes(backers_count, log(pledged))) +
                                   geom_point(aes(color = categories)) +
                                   geom_smooth(se = FALSE) +
                                   facet_wrap(~status) +
                                   labs(x = "Number of Backers", y = "Amount Pledged ($)", 
                                        color = "Categories", 
                                        title = "Number of campaign backers and money pledged", 
                                        subtitle = glue::glue("Kickstarter data for the state of {.y}")) +
                                        #Great job with labeling the plots!
                                   scale_color_OkabeIto() +
                                   theme_minimal() +
                                   theme(plot.title = element_text(face = "bold", hjust = 0.5), 
                                   plot.subtitle = element_text(hjust = 0.5),
                                   legend.position = "bottom",
                                   legend.title = element_text(face = "bold"),
                                   axis.title = element_text(face = "bold"))))

#It might be helpful to label what list/data this calls for quick reference

#Do you think that the smooth line is too similar a color to the technology Kickstarters?
lower48_nest[[3]][4]

#Also this plot is incredibly informative! I did not realize that the number of backers appears to be more vital to a Kickstarter's success than the average pledge per person. Perhaps, you all could report the average pledge/number of pledgers in a separate table for reference?

#While a Shiny app might be more complicated, I think an interactive map of the US/radio button selection with the related Kickstarter plot would be awesome!
```

```{r functionadd}
check_args <- function(data, 
              group_var, 
              sum_var
              ) {
	if(!is.data.frame(data)) {
		stop("Data supplied must be of type data frame.  Data supplied is not a data frame.")
	}
	if(!is.numeric(pull(data, !!enquo(sum_var)))) {
		stop("The variable to summarize must be numeric. The variable supplied is not numeric.")
	}
	if(is.numeric(pull(data, !!enquo(group_var)))) {
		warning("Warning: the grouping variable supplied is numeric, not categorical.")
	}
}

stat_calc <- function(data, 
                      group_var, 
                      outcome_var, 
                      .funs = list(n = ~length(.),
                                   n_valid = ~sum(!is.na(.)),
                                   n_miss = ~sum(is.na(.)),
                                   mean = ~mean(., na.rm = TRUE),
                                   sd = ~sd(., na.rm = TRUE),
                                   min = ~min(., na.rm = TRUE),
                                   max = ~max(., na.rm = TRUE))){
      
              check_args(data, !!enquo(group_var), !!enquo(outcome_var))
  
              data %>%
              	   group_by(!!enquo(group_var)) %>%
                	 summarize_at(vars(!!enquo(outcome_var)),
              		              .funs) #Nice application of class content!
}



#Apologies if I missed it within the project, but I'm not seeing the specific table associated with this function for your lower48 data. 
```

#Overall comments

Areas of strength
1) Effective cleaning and transforming of data for analyses.
2) Very informative and interesting plots that were well-integrated into the code!
3) Efficient functions that do one job, but one job well done.
 
What did I learn?
1) Due to your clear plots, I learned about the importnace of the number of pledgers/average pledge per person in the overall success of a Kickstarter, which was especially evident among "publishing" ones.

Area of improvement
1) Although the code appears to be clear, I think it would benefit further from annotating each step (e.g., splitting data by state).


